Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-20 protocol.tex
Changes to discussion sections, minor typo fixes elsewhere

%-------------------------------------------------------------------------- sub
\subsection{Key Schedule}
\label{sec:keysched}
As mentioned above, the second and third messages of \mEdhoc{} contain
authenticating information.
%
This information is either a signature or a message authentication code (MAC),
as we will describe in more detail in Section~\ref{sec:edhocauth}.
%
The keys for these are generated by using a key schedule which takes at least
one DH key \mGxy{} as basic input, as shown in Figure~\ref{fig:kdfdiagram},
and is intrinsic to the functioning of \mEdhoc{}.
%
\begin{figure}[!h]
\scalebox{.785}{
\input{kdfdiagram.tex}
}
\caption{Key schedule: $P_e, P_I, P_R$ are the DH keys, \mPRKtwo, \mPRKthree,
\mPRKfour{} is the intermediate key material, and
\mKtwoe,\mKtwom, \mKthreeae, \mKthreem{} are the encryption keys for \mAead{}
or \mXor{}.
Dashed boxes are conditionals.~\cite{Norr21}}
\label{fig:kdfdiagram}
\end{figure}
%

>>>>

%-------------------------------------------------------------------------- sub
\subsection{Key Schedule}
\label{sec:keysched}
As mentioned above, the second and third messages of \mEdhoc{} contain
authenticating information.
%
This information is either a signature or a message authentication code (MAC),
as we will describe in more detail in Section~\ref{sec:edhocauth}.
%
The keys for these are generated by using a key schedule which takes at least
one DH key \mGxy{} as basic input, as shown in Figure~\ref{fig:kdfdiagram},
and is intrinsic to the functioning of \mEdhoc{}.
%
\begin{figure}[!h]
\scalebox{.785}{
\input{kdfdiagram.tex}
}
\caption{Key schedule: $P_e, P_I, P_R$ are the DH keys, \mPRKtwo, \mPRKthree, \mPRKfour{} are the intermediate key material, and \mKtwoe,\mKtwom, \mKthreeae, \mKthreem{} are the encryption keys for \mAead{} or \mXor{}. Dashed boxes are conditionals.~\cite{Norr21}}
\label{fig:kdfdiagram}
\end{figure}
%
